Duration Analysis for Non-Expressive performances

### 2021-07-06 material/expstimuli/analysis/stim_n/duration.Rmd
add comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r cv_box, echo = FALSE}
cv_trial <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]

>>>>

#### Box plot
```{r cv_box, echo = FALSE}
cv_trial <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
